\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}

% Page layout
\geometry{
    left=1in,
    right=1in,
    top=1in,
    bottom=1in
}

% Remove page numbering
\pagestyle{empty}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

% Section formatting
\titleformat{\section}
    {\large\bfseries\uppercase}
    {}
    {0pt}
    {}
    [\titlerule]

% Custom spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}

% Header
\begin{center}
    {\Huge\textbf{SAMUEL BAKST}} \\[0.3cm]
    07979147817 $\diamond$ London, UK \\
    \href{mailto:samuel.bakst@yahoo.co.uk}{samuel.bakst@yahoo.co.uk} $\diamond$ \href{https://linkedin.com/in/samuel-bakst}{LinkedIn}
\end{center}

\vspace{0.5cm}

% Professional summary
As an economist with a strong foundation in macroeconomic research and forecasting, I leverage advanced econometric techniques to interpret global economic trends and inform strategic insights. With both a master's and a bachelor's degree in economics, I am now seeking to further my research in economics within the field of artificial intelligence, data science and macroeconomics.

\section{Education}

\textbf{Economics (MSc.)}, UCL \hfill 2022 - 2023
\begin{itemize}[leftmargin=1.5em]
    \item Distinction including a distinction in my dissertation (83\%).
    \item The dissertation titled \textit{Spreading the news; how central banks transmit narrative through the print media} used machine learning to estimate how sentiment is conveyed from the central bank via the media to financial markets.
    \item Courses: Microeconomics, Macroeconomics, Econometrics, Dissertation, Topics in Money \& Finance, Time-Series Econometrics, Macroeconomic policy, Machine Learning for Economics.
\end{itemize}

\textbf{Economics (BSc.)}, University of Bristol \hfill 2019 - 2022
\begin{itemize}[leftmargin=1.5em]
    \item First class with honours including a first class in my dissertation (71\%).
    \item The Applied Economics Dissertation researched the causal effect of inequality on growth.
    \item Courses: Macroeconomics, Microeconomics, Econometrics, Applied Economics Dissertation, Growth \& Development, Applied Microeconomics, Data Science, Behavioural Economics, Public Economics.
\end{itemize}

\section{Experience}

\textbf{Economist} \hfill Sep 2023 - Present \\
\href{https://oxfordeconomics.com/}{Oxford Economics} \hfill \textit{London, UK}
\begin{itemize}[leftmargin=1.5em]
    \item An economist in the Eurozone macro team. Working on research and forecasting our Eurozone outlook.
    \item OECD country economist responsible for the macro forecast and research of Israel.
    \item Energy economist covering the oil, gas, electricity, and coal markets. Responsible for setting our energy market forecasts for all our services in conjunction with our global macro outlook. Primarily, I am responsible for our oil \& gas price forecasts as well as their market fundamentals and balances.
    \item Consumer goods economist in the Industry team, responsible for forecasting and research in the sector.
\end{itemize}

\textbf{LNG Analyst} \hfill Jun 2022 - Aug 2022 \\
\href{https://woodmac.com/}{Wood Mackenzie} \hfill \textit{London, UK}
\begin{itemize}[leftmargin=1.5em]
    \item 9-week summer internship in the liquified natural gas (LNG) \& assets team.
\end{itemize}

\textbf{LNG Analyst} \hfill Jun 2021 - Aug 2021 \\
\href{https://woodmac.com/}{Wood Mackenzie} \hfill \textit{London, UK}
\begin{itemize}[leftmargin=1.5em]
    \item 10-week summer internship in the short-term liquified natural gas (LNG) team.
    \item Produced a price regression model to understand the indexation of LNG contracts to Brent.
\end{itemize}

\textbf{Year in Industry (YINI) student} \hfill Sep 2018 - Aug 2019 \\
\href{https://quod.com/}{Quod} \hfill \textit{London, UK}
\begin{itemize}[leftmargin=1.5em]
    \item I worked in the Socio-economic team that consults on the socio-economic impacts of developments and infrastructure projects and on how to mitigate the effects.
\end{itemize}

\section{Competitions}

\textbf{FocusEconomics Forecast Awards 2025} \hfill 07.2025 \\
1\textsuperscript{st} place for the Israel exchange rate forecast in 2024 \hfill \textit{London, UK}

\section{Additional Information}

\textbf{Investing:} \quad I actively manage my private investment portfolio with a focus on long-term value investing \\
\textbf{Skills:} \quad\quad\quad Presenting, Leadership, Macroeconomic data, Research, HAVER \\
\textbf{Coding:} \quad\quad\; Excel, Python, R, QGIS, HTML, CSS, STATA, EViews and \LaTeX \\
\textbf{Blog:} \quad\quad\quad\; I write a blog called The Economics Book Club

\end{document}